An Extendable \proglang{Python} Implementation of Robust Optimisation Monte Carlo

### 2021-08-24 latex_files/ch2/2_2_LFI_background.tex
plots after changes

An implicit or simulator-based model is a parameterised stochastic
data generating mechanism. The key characteristic of these models is
that we can sample, or simulate, data points, but that we cannot
evaluate the likelihood of a specific set of observations
$\data$. Formally, a simulator-based model is a parameterised family
of probability density functions $\{ p(\yb|\thetab) \}_{\thetab}$,
whose closed-form is either unknown or computationally intractable to
evaluate. Whereas evaluating $p(\yb|\thetab)$ is intractable, sampling
is feasible. Practically, a simulator can be understood as a random black-box
machine (computer code) $M_r$ that generates samples $\yb$ in a stochastic manner for
any given a set of parameters $\thetab$. We can isolate the randomness by introducing the stochastic nuisance variables $\vb \sim p(\vb)$ so that the simulator becomes a deterministic mapping $M_d$ that maps $(\thetab, \vb)$ to the data $\yb$. The distribution $p(\vb)$ is determined by the random draws performed when running $M_r$. Importantly, we can fix the value of $\vb$ while changing $\thetab$ by fixing the random seed used with $M_r$.

>>>>

An implicit or simulator-based model is a parameterised stochastic
data generating mechanism. The key characteristic of these models is
that we can sample, or simulate, data points, but that we cannot
evaluate the likelihood of a specific set of observations
$\data$. Formally, a simulator-based model is a parameterised family
of probability density functions $\{ p(\yb|\thetab) \}_{\thetab}$,
whose closed-form is either unknown or computationally
intractable. Whereas evaluating $p(\yb|\thetab)$ is intractable,
sampling is feasible. Practically, a simulator can be understood as a
random black-box machine (computer code) $M_r$ that generates samples
$\yb$ in a stochastic manner for any given a set of parameters
$\thetab$. We can isolate the randomness by introducing the stochastic
nuisance variables $\vb \sim p(\vb)$ so that the simulator becomes a
deterministic mapping $M_d$ that maps $(\thetab, \vb)$ to the data
$\yb$. The distribution $p(\vb)$ is determined by the random draws
performed when running $M_r$. Importantly, we can fix the value of
$\vb$ while changing $\thetab$ by fixing the random seed used with
$M_r$.

### 2021-08-24 latex_files/ch2/2_4_ROMC.tex
applied fixes
minor improvements
plots after changes

ROMC resolves the failure-modes of OMC mainly by approaching the
acceptance regions $\mathcal{S}_i$ in a more sophisticated
way. Instead of collapsing the acceptance regions into single points,
we approximate them with a bounding box region. A uniform distribution
defined on the bounding box area, is then used as the \emph{proposal
  distribution} for importance sampling. If $q_i$ is the uniform
distribution defined on the $i-th$ bounding box, weighted sampling is
performed by drawing samples from $q_i$ and assigning the weights as
in~\eqref{eq:sampling}.

@@

\subsubsection{Proposal region estimation}

@@

For each set of nuisance variables $\vb_i, i = \{1,2,\ldots,n_1 \}$ a
deterministic function is defined as
$f_i(\thetab) = M_d(\thetab,\vb_i)$. We look for a point
$\thetab_* : d(f_i(\thetab_*), \data) < \epsilon$. This point can be
obtained by solving the the following optimisation problem:

\begin{subequations}
\begin{alignat}{2}
&\!\min_{\thetab}        &\qquad& g_i(\thetab) = d(\data,  f_i(\thetab))\label{eq:optProb}\\
&\text{subject to} &      & g_i(\thetab) \leq \epsilon
\end{alignat}
\end{subequations}
%
The optimisation problem can be treated as unconstrained, accepting
the optimal point $\thetab_i^* = \text{argmin}_{\thetab} g_i(\thetab)$
only if $g_i(\thetab_i^*) < \epsilon$. The nature of the generative
model $M_r(\thetab)$, specifies the properties of the objective
function $g_i$. If $g_i$ is differentiable any gradient-based
iterative algorithm can be used for~\ref{eq:optProb}. The gradients
$\nabla_{\thetab} g_i$ can be either provided in closed form or
approximated by finite differences. Alternatively, if $g_i$ is not
differentiable, the Bayesian Optimisation approach provides an
alternative choice~\cite{Shahriari2016}. In this case, apart from
obtaining an optimal $\thetab_i^* $, a surrogate model $\hat{d}_i$ of
the distance $g_i$ is also fitted; the approximate model can then
substitute the actual model in the following steps, e.g. construction
of bounding box, sampling, for accelerating the method.

\subsubsection*{Bounding boxes construction}

After obtaining a $\thetab_i^*$ such that
$g_i(\thetab_i^*) < \epsilon$, we need to construct a bounding box
area $\mathcal{\hat{S}}_i$ around it. The bounding box must contain
the acceptance region around $\thetab_i^*$, formally
$\{ \thetab : g_i(\thetab) < \epsilon$,
$d(\thetab, \thetab_i^*) < M \}$. The second condition
$d(\thetab, \thetab_i^*) < M$ describes that if
$\mathcal{S}_i := \{ \thetab : g_i(\thetab) < \epsilon \} $ contains a
number of disjoint sets of $\thetab$ that they fulfill
$g_i(\thetab) < \epsilon$, we want the bounding box to match only the
set that contains $\thetab_i^*$. We seek for a bounding box that is as
tight as possible to the local acceptance region for ensuring high
acceptance rate in the importance sampling.

Bounding boxes are built in two steps. Firstly, the search directions
$\mathbf{v}_d$ are computed as the eigenvectors of the curvature at
$\thetab_i^*$ and then the limits are obtained with a line-search
method looking for the smallest
$\kappa: g_i(\thetab_i^* + \kappa \vb_d) \geq
\epsilon$\footnote{$-\kappa$ is used as well for the opposite
  direction along the search line}. The
Algorithm~\ref{alg:region_construction} describes the method
in-depth. After limits are found along all directions the uniform
distribution $q_i$ can be defined and is used as the proposal region
for importance sampling.

>>>>

ROMC resolves the failure-modes of OMC mainly by approaching the
acceptance regions $\mathcal{S}_i$ in a more sophisticated
way. Instead of collapsing the acceptance regions into single points,
it approximates them with a bounding box region. A uniform distribution
defined on the bounding box area, is then used as the \emph{proposal
  distribution} for importance sampling. If $q_i$ is the uniform
distribution defined on the $i-th$ bounding box, weighted sampling is
performed by drawing samples from $q_i$ and assigning the weights as
in~\eqref{eq:sampling}.

@@

@@

For each set of nuisance variables $\vb_i, i = \{1,2,\ldots,n_1 \}$,
we search for a point $\thetab^*$ such that
$d(M_d(\thetab^*,\vb_i), \data) < \epsilon$. For notation convenience,
we name the function $d(M_d(\thetab^*,\vb_i)$ as $d_i(\thetab)$.  Obtaining
this point involves solving the following optimisation problem:

\begin{subequations}
\begin{alignat}{2}
  &\!\min_{\thetab}        &\qquad& d_i(\thetab) = d(M_d(\thetab^*,\vb_i), \data)\label{eq:optProb}\\
  &\text{subject to} & & d_i(\thetab) \leq \epsilon
\end{alignat}
\end{subequations}
%
The optimisation problem can be treated as unconstrained, accepting
the optimal point $\thetab_i^* = \text{argmin}_{\thetab} d_i(\thetab)$
only if $d_i(\thetab_i^*) < \epsilon$. The nature of the generative
model $M_r(\thetab)$, specifies the properties of the objective
function $d_i$. If $d_i$ is differentiable any gradient-based
iterative algorithm can be used for~\ref{eq:optProb}. The gradients
$\nabla_{\thetab} g_i$ can be either provided in closed form or
approximated by finite differences. Alternatively, if $d_i$ is not
differentiable, the Bayesian Optimisation approach provides an
alternative choice~\cite{Shahriari2016}. In this case, apart from
obtaining an optimal $\thetab_i^* $, a surrogate model $\hat{d}_i$ of
the distance $d_i$ is also fitted; the approximate model can then
substitute the actual model in the following steps.

\subsubsection*{Proposal region computation}

After obtaining $\thetab_i^*$, we approximate the acceptance region
$\mathcal{S}_i$ by constructing a bounding box $\mathcal{\hat{S}}_i$
around it. The bounding must the part of the acceptance region
$\mathcal{S}_i$ around $\thetab_i^*$, formally
$\{ \thetab : d_i(\thetab) < \epsilon$,
$d(\thetab, \thetab_i^*) < M \}$. The second condition
$d(\thetab, \thetab_i^*) < M$ describes that if
$\mathcal{S}_i := \{ \thetab : d_i(\thetab) < \epsilon \} $ contains a
number of disjoint sets of $\thetab$ that they fulfill
$d_i(\thetab) < \epsilon$, we want the bounding box to match only the
set that contains $\thetab_i^*$. We seek for a bounding box that is as
tight as possible to the local acceptance region for ensuring high
acceptance rate in the importance sampling.

Bounding boxes are built in two steps. Firstly, the search directions
$\mathbf{v}_d$ are computed as the eigenvectors of the curvature at
$\thetab_i^*$ and then the limits are obtained with a line-search
method looking for the smallest
$\kappa: d_i(\thetab_i^* + \kappa \vb_d) \geq
\epsilon$\footnote{$-\kappa$ is used as well for the opposite
  direction along the search line}. The
Algorithm~\ref{alg:region_construction} describes the method
in-depth. After limits are found along all directions the uniform
distribution $q_i$ can be defined and is used as the proposal region
for importance sampling.

### 2021-08-24 latex_files/images/chapter3/example_marginal.tex
plots after changes

% This file was created by tikzplotlib v0.9.9.
\begin{tikzpicture}

@@

\draw[draw=none,fill=color0] (axis cs:-2.57142857142857,0) rectangle (axis cs:-2.48571428571429,0.00722007830101246);
\draw[draw=none,fill=color0] (axis cs:-2.48571428571429,0) rectangle (axis cs:-2.4,0.0252702740535435);
\draw[draw=none,fill=color0] (axis cs:-2.4,0) rectangle (axis cs:-2.31428571428571,0.0347466268236223);
\draw[draw=none,fill=color0] (axis cs:-2.31428571428571,0) rectangle (axis cs:-2.22857142857143,0.0374541561865022);
\draw[draw=none,fill=color0] (axis cs:-2.22857142857143,0) rectangle (axis cs:-2.14285714285714,0.0510691609826969);
\draw[draw=none,fill=color0] (axis cs:-2.14285714285714,0) rectangle (axis cs:-2.05714285714286,0.0647744167576544);
\draw[draw=none,fill=color0] (axis cs:-2.05714285714286,0) rectangle (axis cs:-1.97142857142857,0.080503873056289);
\draw[draw=none,fill=color0] (axis cs:-1.97142857142857,0) rectangle (axis cs:-1.88571428571429,0.089941546835469);
\draw[draw=none,fill=color0] (axis cs:-1.88571428571429,0) rectangle (axis cs:-1.8,0.113625982262183);
\draw[draw=none,fill=color0] (axis cs:-1.8,0) rectangle (axis cs:-1.71428571428571,0.12614508231626);
\draw[draw=none,fill=color0] (axis cs:-1.71428571428571,0) rectangle (axis cs:-1.62857142857143,0.145794009692587);
\draw[draw=none,fill=color0] (axis cs:-1.62857142857143,0) rectangle (axis cs:-1.54285714285714,0.171554217630842);
\draw[draw=none,fill=color0] (axis cs:-1.54285714285714,0) rectangle (axis cs:-1.45714285714286,0.157720031886223);
\draw[draw=none,fill=color0] (axis cs:-1.45714285714286,0) rectangle (axis cs:-1.37142857142857,0.174635643905738);
\draw[draw=none,fill=color0] (axis cs:-1.37142857142857,0) rectangle (axis cs:-1.28571428571429,0.199983275941078);
\draw[draw=none,fill=color0] (axis cs:-1.28571428571429,0) rectangle (axis cs:-1.2,0.216744171997);
\draw[draw=none,fill=color0] (axis cs:-1.2,0) rectangle (axis cs:-1.11428571428571,0.240854076323595);
\draw[draw=none,fill=color0] (axis cs:-1.11428571428571,0) rectangle (axis cs:-1.02857142857143,0.277844084619317);
\draw[draw=none,fill=color0] (axis cs:-1.02857142857143,0) rectangle (axis cs:-0.942857142857143,0.253682608304859);
\draw[draw=none,fill=color0] (axis cs:-0.942857142857143,0) rectangle (axis cs:-0.857142857142857,0.2729834247631);
\draw[draw=none,fill=color0] (axis cs:-0.857142857142857,0) rectangle (axis cs:-0.771428571428571,0.303178823657691);
\draw[draw=none,fill=color0] (axis cs:-0.771428571428571,0) rectangle (axis cs:-0.685714285714285,0.297596155971373);
\draw[draw=none,fill=color0] (axis cs:-0.685714285714285,0) rectangle (axis cs:-0.6,0.292864426084818);
\draw[draw=none,fill=color0] (axis cs:-0.6,0) rectangle (axis cs:-0.514285714285714,0.327185584008558);
\draw[draw=none,fill=color0] (axis cs:-0.514285714285714,0) rectangle (axis cs:-0.428571428571428,0.303294860630386);
\draw[draw=none,fill=color0] (axis cs:-0.428571428571428,0) rectangle (axis cs:-0.342857142857143,0.313867118142585);
\draw[draw=none,fill=color0] (axis cs:-0.342857142857143,0) rectangle (axis cs:-0.257142857142857,0.316600433499394);
\draw[draw=none,fill=color0] (axis cs:-0.257142857142857,0) rectangle (axis cs:-0.171428571428571,0.325419243424203);
\draw[draw=none,fill=color0] (axis cs:-0.171428571428571,0) rectangle (axis cs:-0.0857142857142859,0.322737500055257);
\draw[draw=none,fill=color0] (axis cs:-0.0857142857142859,0) rectangle (axis cs:0,0.331556309980064);
\draw[draw=none,fill=color0] (axis cs:0,0) rectangle (axis cs:0.0857142857142859,0.327533694926642);
\draw[draw=none,fill=color0] (axis cs:0.0857142857142859,0) rectangle (axis cs:0.171428571428571,0.351940138183459);
\draw[draw=none,fill=color0] (axis cs:0.171428571428571,0) rectangle (axis cs:0.257142857142857,0.308245771465366);
\draw[draw=none,fill=color0] (axis cs:0.257142857142857,0) rectangle (axis cs:0.342857142857143,0.329080854562574);
\draw[draw=none,fill=color0] (axis cs:0.342857142857143,0) rectangle (axis cs:0.428571428571429,0.311752666640144);
\draw[draw=none,fill=color0] (axis cs:0.428571428571429,0) rectangle (axis cs:0.514285714285714,0.312139456549128);
\draw[draw=none,fill=color0] (axis cs:0.514285714285714,0) rectangle (axis cs:0.6,0.322673035070425);
\draw[draw=none,fill=color0] (axis cs:0.6,0) rectangle (axis cs:0.685714285714286,0.302650210782081);
\draw[draw=none,fill=color0] (axis cs:0.685714285714286,0) rectangle (axis cs:0.771428571428571,0.313763974166856);
\draw[draw=none,fill=color0] (axis cs:0.771428571428571,0) rectangle (axis cs:0.857142857142857,0.278656343428181);
\draw[draw=none,fill=color0] (axis cs:0.857142857142857,0) rectangle (axis cs:0.942857142857143,0.269785961515508);
\draw[draw=none,fill=color0] (axis cs:0.942857142857143,0) rectangle (axis cs:1.02857142857143,0.245830773152508);
\draw[draw=none,fill=color0] (axis cs:1.02857142857143,0) rectangle (axis cs:1.11428571428571,0.227754791406045);
\draw[draw=none,fill=color0] (axis cs:1.11428571428571,0) rectangle (axis cs:1.2,0.218858623499437);
\draw[draw=none,fill=color0] (axis cs:1.2,0) rectangle (axis cs:1.28571428571429,0.218433154599559);
\draw[draw=none,fill=color0] (axis cs:1.28571428571429,0) rectangle (axis cs:1.37142857142857,0.21010427855946);
\draw[draw=none,fill=color0] (axis cs:1.37142857142857,0) rectangle (axis cs:1.45714285714286,0.193691493421625);
\draw[draw=none,fill=color0] (axis cs:1.45714285714286,0) rectangle (axis cs:1.54285714285714,0.194078283330608);
\draw[draw=none,fill=color0] (axis cs:1.54285714285714,0) rectangle (axis cs:1.62857142857143,0.130644738257426);
\draw[draw=none,fill=color0] (axis cs:1.62857142857143,0) rectangle (axis cs:1.71428571428571,0.150177628661059);
\draw[draw=none,fill=color0] (axis cs:1.71428571428571,0) rectangle (axis cs:1.8,0.0986572127845487);
\draw[draw=none,fill=color0] (axis cs:1.8,0) rectangle (axis cs:1.88571428571429,0.0960012554095325);
\draw[draw=none,fill=color0] (axis cs:1.88571428571429,0) rectangle (axis cs:1.97142857142857,0.0732709017583105);
\draw[draw=none,fill=color0] (axis cs:1.97142857142857,0) rectangle (axis cs:2.05714285714286,0.0897223658870459);
\draw[draw=none,fill=color0] (axis cs:2.05714285714286,0) rectangle (axis cs:2.14285714285714,0.0617058834797238);
\draw[draw=none,fill=color0] (axis cs:2.14285714285714,0) rectangle (axis cs:2.22857142857143,0.0434622927727019);
\draw[draw=none,fill=color0] (axis cs:2.22857142857143,0) rectangle (axis cs:2.31428571428571,0.0347466268236225);
\draw[draw=none,fill=color0] (axis cs:2.31428571428571,0) rectangle (axis cs:2.4,0.0374541561865018);
\draw[draw=none,fill=color0] (axis cs:2.4,0) rectangle (axis cs:2.48571428571429,0.0320390974607428);
\draw[draw=none,fill=color0] (axis cs:2.48571428571429,0) rectangle (axis cs:2.57142857142857,0.00496380383194607);

>>>>

% This file was created with tikzplotlib v0.9.12.
\begin{tikzpicture}

@@

\draw[draw=none,fill=color0] (axis cs:-2.57142857142857,0) rectangle (axis cs:-2.48571428571429,0.006208033765389);
\draw[draw=none,fill=color0] (axis cs:-2.48571428571429,0) rectangle (axis cs:-2.4,0.0261624280112821);
\draw[draw=none,fill=color0] (axis cs:-2.4,0) rectangle (axis cs:-2.31428571428571,0.0337007547263973);
\draw[draw=none,fill=color0] (axis cs:-2.31428571428571,0) rectangle (axis cs:-2.22857142857143,0.0363613406258499);
\draw[draw=none,fill=color0] (axis cs:-2.22857142857143,0) rectangle (axis cs:-2.14285714285714,0.0541896684870789);
\draw[draw=none,fill=color0] (axis cs:-2.14285714285714,0) rectangle (axis cs:-2.05714285714286,0.0670526704061584);
\draw[draw=none,fill=color0] (axis cs:-2.05714285714286,0) rectangle (axis cs:-1.97142857142857,0.0841007399119992);
\draw[draw=none,fill=color0] (axis cs:-1.97142857142857,0) rectangle (axis cs:-1.88571428571429,0.0882637860955287);
\draw[draw=none,fill=color0] (axis cs:-1.88571428571429,0) rectangle (axis cs:-1.8,0.107105098505383);
\draw[draw=none,fill=color0] (axis cs:-1.8,0) rectangle (axis cs:-1.71428571428571,0.134226458530087);
\draw[draw=none,fill=color0] (axis cs:-1.71428571428571,0) rectangle (axis cs:-1.62857142857143,0.13742807026801);
\draw[draw=none,fill=color0] (axis cs:-1.62857142857143,0) rectangle (axis cs:-1.54285714285714,0.172328991470496);
\draw[draw=none,fill=color0] (axis cs:-1.54285714285714,0) rectangle (axis cs:-1.45714285714286,0.159523545491678);
\draw[draw=none,fill=color0] (axis cs:-1.45714285714286,0) rectangle (axis cs:-1.37142857142857,0.181085502173434);
\draw[draw=none,fill=color0] (axis cs:-1.37142857142857,0) rectangle (axis cs:-1.28571428571429,0.198590015309879);
\draw[draw=none,fill=color0] (axis cs:-1.28571428571429,0) rectangle (axis cs:-1.2,0.221267556259859);
\draw[draw=none,fill=color0] (axis cs:-1.2,0) rectangle (axis cs:-1.11428571428571,0.234145572772051);
\draw[draw=none,fill=color0] (axis cs:-1.11428571428571,0) rectangle (axis cs:-1.02857142857143,0.277788991057236);
\draw[draw=none,fill=color0] (axis cs:-1.02857142857143,0) rectangle (axis cs:-0.942857142857143,0.250781241453748);
\draw[draw=none,fill=color0] (axis cs:-0.942857142857143,0) rectangle (axis cs:-0.857142857142857,0.265410460009239);
\draw[draw=none,fill=color0] (axis cs:-0.857142857142857,0) rectangle (axis cs:-0.771428571428571,0.303461442846629);
\draw[draw=none,fill=color0] (axis cs:-0.771428571428571,0) rectangle (axis cs:-0.685714285714285,0.302778779346469);
\draw[draw=none,fill=color0] (axis cs:-0.685714285714285,0) rectangle (axis cs:-0.6,0.294470204004708);
\draw[draw=none,fill=color0] (axis cs:-0.6,0) rectangle (axis cs:-0.514285714285714,0.32589124301026);
\draw[draw=none,fill=color0] (axis cs:-0.514285714285714,0) rectangle (axis cs:-0.428571428571428,0.307263137822596);
\draw[draw=none,fill=color0] (axis cs:-0.428571428571428,0) rectangle (axis cs:-0.342857142857143,0.310432718428548);
\draw[draw=none,fill=color0] (axis cs:-0.342857142857143,0) rectangle (axis cs:-0.257142857142857,0.313571769361836);
\draw[draw=none,fill=color0] (axis cs:-0.257142857142857,0) rectangle (axis cs:-0.171428571428571,0.322468416267153);
\draw[draw=none,fill=color0] (axis cs:-0.171428571428571,0) rectangle (axis cs:-0.0857142857142859,0.329442694767694);
\draw[draw=none,fill=color0] (axis cs:-0.0857142857142859,0) rectangle (axis cs:0,0.328704477273017);
\draw[draw=none,fill=color0] (axis cs:0,0) rectangle (axis cs:0.0857142857142859,0.315996626149429);
\draw[draw=none,fill=color0] (axis cs:0.0857142857142859,0) rectangle (axis cs:0.171428571428571,0.35869562652787);
\draw[draw=none,fill=color0] (axis cs:0.171428571428571,0) rectangle (axis cs:0.257142857142857,0.299321419039204);
\draw[draw=none,fill=color0] (axis cs:0.257142857142857,0) rectangle (axis cs:0.342857142857143,0.327344655623505);
\draw[draw=none,fill=color0] (axis cs:0.342857142857143,0) rectangle (axis cs:0.428571428571429,0.324602990921247);
\draw[draw=none,fill=color0] (axis cs:0.428571428571429,0) rectangle (axis cs:0.514285714285714,0.300242814569848);
\draw[draw=none,fill=color0] (axis cs:0.514285714285714,0) rectangle (axis cs:0.6,0.325196567835609);
\draw[draw=none,fill=color0] (axis cs:0.6,0) rectangle (axis cs:0.685714285714286,0.3008173729996);
\draw[draw=none,fill=color0] (axis cs:0.685714285714286,0) rectangle (axis cs:0.771428571428571,0.306931815801259);
\draw[draw=none,fill=color0] (axis cs:0.771428571428571,0) rectangle (axis cs:0.857142857142857,0.292671455749884);
\draw[draw=none,fill=color0] (axis cs:0.857142857142857,0) rectangle (axis cs:0.942857142857143,0.266064095296049);
\draw[draw=none,fill=color0] (axis cs:0.942857142857143,0) rectangle (axis cs:1.02857142857143,0.241445667943122);
\draw[draw=none,fill=color0] (axis cs:1.02857142857143,0) rectangle (axis cs:1.11428571428571,0.23182281521762);
\draw[draw=none,fill=color0] (axis cs:1.11428571428571,0) rectangle (axis cs:1.2,0.217147051423478);
\draw[draw=none,fill=color0] (axis cs:1.2,0) rectangle (axis cs:1.28571428571429,0.224310513797232);
\draw[draw=none,fill=color0] (axis cs:1.28571428571429,0) rectangle (axis cs:1.37142857142857,0.212377916164659);
\draw[draw=none,fill=color0] (axis cs:1.37142857142857,0) rectangle (axis cs:1.45714285714286,0.190746892354591);
\draw[draw=none,fill=color0] (axis cs:1.45714285714286,0) rectangle (axis cs:1.54285714285714,0.196218210084616);
\draw[draw=none,fill=color0] (axis cs:1.54285714285714,0) rectangle (axis cs:1.62857142857143,0.133681428800119);
\draw[draw=none,fill=color0] (axis cs:1.62857142857143,0) rectangle (axis cs:1.71428571428571,0.142913401618273);
\draw[draw=none,fill=color0] (axis cs:1.71428571428571,0) rectangle (axis cs:1.8,0.108955396863223);
\draw[draw=none,fill=color0] (axis cs:1.8,0) rectangle (axis cs:1.88571428571429,0.0924363415213623);
\draw[draw=none,fill=color0] (axis cs:1.88571428571429,0) rectangle (axis cs:1.97142857142857,0.0739859090188589);
\draw[draw=none,fill=color0] (axis cs:1.97142857142857,0) rectangle (axis cs:2.05714285714286,0.0907797314146689);
\draw[draw=none,fill=color0] (axis cs:2.05714285714286,0) rectangle (axis cs:2.14285714285714,0.0652904576612423);
\draw[draw=none,fill=color0] (axis cs:2.14285714285714,0) rectangle (axis cs:2.22857142857143,0.0433796619328517);
\draw[draw=none,fill=color0] (axis cs:2.22857142857143,0) rectangle (axis cs:2.31428571428571,0.0363613406258499);
\draw[draw=none,fill=color0] (axis cs:2.31428571428571,0) rectangle (axis cs:2.4,0.0359179096426075);
\draw[draw=none,fill=color0] (axis cs:2.4,0) rectangle (axis cs:2.48571428571429,0.0301533068604609);
\draw[draw=none,fill=color0] (axis cs:2.48571428571429,0) rectangle (axis cs:2.57142857142857,0.00665146474863107);
